Models

### 2023-06-23 analysis/05_model_metrics.Rmd
Save out the missing models

#Fit with a different algorithm
bad_indv_results2 <- pmap_dfr(bad_indv_models2 %>% select(-warning), get_model, data = model_data, control = lmerControl(optimizer = "bobyqa")) %>%
  mutate(REML = TRUE, bobyqa = TRUE)

# There are 12 study/metric combos that can't be fit due to data limitations (too many rarefyID's )
# tofit_mods <- bad_indv_results2 %>% filter(!is.na(warning)) %>% select(metric, study_id, formula) %>% distinct()
# 
# missing_indv_studies <- pmap_df(tofit_mods %>% select(metric_name = metric, filter_study_id = study_id), function(metric_name, filter_study_id) {model_data %>%
#          filter(metric_name == metric, study_id == filter_study_id) %>%
#         mutate(n = n(), nrarefyID = n_distinct(rarefyID)) %>%
#         select(metric, study_id, nrarefyID, n) %>%
#         distinct()})

>>>>

#Fit with a different algorithm
bad_indv_results2 <- pmap_dfr(bad_indv_models2 %>% select(-warning), get_model, data = model_data, control = lmerControl(optimizer = "bobyqa")) %>%
  mutate(REML = TRUE, bobyqa = TRUE)
```

There are 12 study/metric combos that can't be fit due to data limitations (too many rarefyID's )
```{r}
tofit_mods <- bad_indv_results2 %>% filter(!is.na(warning)) %>% select(metric, study_id, formula) %>% distinct()

missing_indv_studies <- pmap_df(tofit_mods %>% select(metric_name = metric, filter_study_id = study_id), function(metric_name, filter_study_id) {model_data %>%
         filter(metric_name == metric, study_id == filter_study_id) %>%
        mutate(n = n(), nrarefyID = n_distinct(rarefyID)) %>%
        select(metric, study_id, nrarefyID, n) %>%
        distinct()})

readr::write_csv(missing_indv_studies, here::here("paper/missing_indv_studies.csv"))
```
